Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-09 journal/article.tex
Small edits

A key question in this study was the definition of \emph{large scale}. Large
scale requires additional coordination and makes communication difficult
compared to software development in small teams. One of the motivations for this
research was to identify phenomena that appear particularly in large-scale
transformations, and which may not be present in small organizations.

@@

To assess the validity of this research internal validity and external validity
needs to be considered. In this section we present the identified threats to
validity and the strategies used to mitigate them. We highlight two specific
limitations in the research: weakness in keyword search, and the strength of
evidence of primary sources.

@@

The second part of the research that may have been affected by subjective bias
was the elicitation of results by coding and analysis. Our tools for mitigating
this threat were limited, as the work stages in question are particularly
laborous and for resource constraints the process could not be duplicated. We
assessed the bias of the coding step using an experiment, and prevented
subjective bias in analysis by making the results as tracable as possible. The
coding experiment revealed that two researchers can find roughly 2 of 3 themes
in an experience report identically. The traceability of results is achieved by
supplying references to each claim presented in the results.

This study had only a minor threat to external validity. The systematic
literature review approach includes steps to identify all studies that may be
relevant in the study area. As long as the systematic approach is adhered to
threats against external validity are minimized. External validity was also
confirmed by saturation of the primary studies. Saturation was evident, as when
the majority of the primary studies had been coded almost all quotations for the
remaining studies could be assigned to existing codes.

A particular problem in this systematic literature review was the limitations of
boolean keyword searches in online databases. A keyword search can not identify
the facet of \emph{large scale}, and also \emph{transformation} is difficult to
capture with keywords. Because of this we assume that it is likely that a some
studies have been missed by the keyword search, potentially causing bias. To
eliminate the potential bias we would suggest combining the entire archive of
\emph{Agile Conference} and \emph{Agile Processes in Software Engineering and
Extreme Programming} to the results of the keyword search. These two conferences
provided more than two thirds of the primary sources.

>>>>

A key question in this study was the definition of \emph{large scale}. Our goal
was to identify phenomena that appear particularly in large-scale
transformations, and which may not be present in small organizations. Large
scale requires additional coordination and makes communication difficult
compared to software development in small teams.

@@

To assess the validity of this research internal validity and external validity
needs to be considered. In this section we present the identified threats to
validity and the strategies used to mitigate them. We also highlight two
specific limitations in the research: weakness in keyword search, and the
strength of evidence of primary sources.

@@

The second part of the research that may have been affected by subjective bias
was the elicitation of results by coding and analysis. Our tools for mitigating
this threat were limited, as the work stages in question are particularly
laborous. For resource constraints the process could not be duplicated. We
assessed the bias of the coding step using an experiment, and prevented
subjective bias in analysis by making the results as tracable as possible. The
coding experiment revealed that two researchers can find roughly 2 of 3 themes
in an experience report identically. Traceability of results was achieved by
supplying references to each claim presented in the results.

This study had a minor threat to external validity. The systematic literature
review approach includes steps to identify all studies that may be relevant in
the study area. As long as the systematic approach is adhered to, including
systematic identification of research, threats against external validity are
minimized. External validity was also confirmed by saturation of the primary
studies. Saturation was evident, as when the majority of the primary studies had
been coded almost all quotations for the remaining studies could be assigned to
existing codes.

A particular problem in this systematic literature review was the limitations of
boolean keyword searches in online databases. A keyword search can not identify
the facet of \emph{large scale}, and also \emph{transformation} is difficult to
capture with keywords. Because of this we assume that it is likely that a some
studies have been missed by the keyword search, potentially causing bias. To
eliminate the potential bias we would suggest manually searching the entire
archive of \emph{Agile Conference} and \emph{Agile Processes in Software
Engineering and Extreme Programming} for relevant studies. These two conferences
provided more than two thirds of the primary sources.
